MLH1 Results Outline

### 2020-03-06 doc/Results.rmd
trying to find pattern for rbar and gamma estimates

>>>>

```{r Q1.rbar, echo=FALSE}
source("~./MLH1repo/src/CommonFunc_MLH1repo.R")

#read.csv of gamma estimates from above
gamma_estimates <- read.csv("~./MLH1repo/results/gamma_estimates.csv", header = TRUE)

table_gamma_estimates <- read.csv("~./MLH1repo/table.csv", header = TRUE)

for(e in 1:length(cleanCurated_BivData$fileName)){
#  mini.IFD <- calq.intra.rbar(mini.IFD)
  cleanCurated_BivData$rbar[e] <- new.calq.intra.rbar(cleanCurated_BivData[e,])
  }

#calq the mouse / strain means for rbar

summarize_rbar_table <- ddply(.data=cleanCurated_BivData,
                 .(sex, strain),
                 summarize,
                 mean.rbar.all = mean(rbar, na.rm = TRUE),

                 mean.rbar.2CO = mean(rbar[which(hand.foci.count == 2)], na.rm = TRUE),
                 mean.rbar.3CO = mean(rbar[which(hand.foci.count == 3)], na.rm = TRUE)
)
#the 3 is negative...

#how best to merge rbar and gamma estiamtes (which estimate)

raw.gamma_estimates <-  gamma_estimates %>% filter(type.IFD == "raw.IFD") %>% filter( (class == "2CO") | (class == "3CO") )

table <- raw.gamma_estimates
write.table(table, "~./MLH1repo/table.csv", sep=",",row.names = TRUE)

write.table(summarize_rbar_table, "~./MLH1repo/RBAR.table.csv", sep=",",row.names = TRUE)

#what comparison of IFD and rbar would be logical
#plot rbar and gamma
ll <- ggplot(table_gamma_estimates, aes(y=mean.rbar, x = all.biv.gamma, color = class, shape = sex ))+geom_point()+facet_wrap(~strain)+ ggtitle("")+ylim(c(0,.5))

#mean rbars are up around 
#SKIVE male have extra (very strong interference)
#there's so much variance across the gamma estimates -- 
#most all females seem to have stronger interfernce
#there don't seem to be consistant patterns
